\vspace*{5pt}
\subsection{{\href{https://www.paloaltonetworks.com/about-us}{Palo Alto Networks} \hfill Jan 2020 --- Current}}
\vspace*{5pt}
{\footnotesize
	\subtext{Principal Security Consultant / Extended Expertise \hfill Remote}
}
\begin{zitemize}
\item Security Transformation and Recovery: Lead the design and deployment of Palo Alto Networks security solutions to drive rapid security transformation for enterprise customers migrating to the cloud.
\item Infrastructure as Code (IaC): Architect and deploy scalable security infrastructure using IaC across GCP, OCI, AWS, and Azure, ensuring that recovery environments adhere to Palo Alto Networks reference architectures and industry best practices.
\item Trusted Advisory: Act as a primary technical advisor to customer account teams and stakeholders, identifying critical policy and technology gaps that enabled security breaches and developing holistic remediation plans.
\item Cross-Functional Collaboration: Collaborate with internal engagement leads and diverse customer contacts, from technical admins to executive leadership, to communicate project status, mitigate risks, and ensure a cohesive post-incident security posture.
\item High-Pressure Execution: Manage complex configuration and troubleshooting tasks in high-stakes environments, remaining composed and articulate while guiding customers through urgent security improvements.
\item Agile Leadership: Designate and guide Agile processes for engineering teams to accelerate the delivery of secure, cloud-native infrastructure and mission-critical updates.
\end{zitemize}

\vspace*{5pt}
\subsection{{\href{https://www.ucdenver.edu}{University of Colorado - Denver} \hfill Sep 2025 --- Current}}
\vspace*{5pt}
{\footnotesize
	\subtext{Faculty Lecturer \hfill Denver, CO}
}
\begin{zitemize}
\item  Guiding students through fundamental concepts of IT infrastructure, data management, and the role of information systems in modern business and technology.
\end{zitemize}

\vspace*{5pt}
\subsection{{\href{https://www.paloaltonetworks.com/about-us}{Salesforce} \hfill Oct 2014 --- Jan 2020}}
\vspace*{5pt}
{\footnotesize
	\subtext{Security Engineer \hfill Bellvue, Washington}
}
\begin{zitemize}
	\item Security Engineer with the Detection and Response Engineering team at Salesforce. My team is based primarily in Bellevue, Washington. I've been working remotely on this team from another part of the US for approximately three years.
	\item My team collects security data and logs from many sources, then normalizes and runs data science models on them to find bad actors in a way that enhances and extends traditional human-based Detection and Response work. My job in particular is to create the automation and pipelines to gather this data, which is often referred to as \#dataengineering . I also work on the CI/CD pipeline and automation of unit and integration testing for tools our broader team has spread across many Git repositories.
\end{zitemize}

\vspace*{5pt}
\subsection{{\href{https://www.paloaltonetworks.com/about-us}{Principal Research Software Engineer} \hfill Aug 2012 --- Jan 2014}}
\vspace*{5pt}
{\footnotesize
	\subtext{Security Engineer \hfill Indiana University, Bloomington IN}
}
\begin{zitemize}
	\item Test Architect in Software Defined Networking Lab, designed test cases and direct test efforts on openflow networks.
	\item Wrote web based tools for GENI/GEMINI project. Assistant instructor for undergraduate networking (lead discussions, create and grade homework, and proctor exams).
	\item Research very high capacity storage solutions and high speed network connections.
\end{zitemize}

\vspace*{5pt}
\subsection{{\href{https://nsn.com}{Nokia Siemens Networks} \hfill Apr 2011 --- Jul 2012}}
\vspace*{5pt}
{\footnotesize
	\subtext{Research And Development Engineer \hfill Espoo, Uusimaa, Finland and Arlington Heights, IL USA}
}
\begin{zitemize}
	\item CDMA Cellular base station product development.
\end{zitemize}

\vspace*{5pt}
\subsection{{\href{https://www.motorolasolutions.com/en_us.html}{Motorola - Cellular Networks and Space Sector} \hfill Jan 1998 --- Mar 2011}}
\vspace*{5pt}
{\footnotesize
	\subtext{Senior Software Engineer \hfill Arlington Heights, IL}
}
\begin{zitemize}
	\item Worked on and with customer accounts teams including Sprint, ALLTEL, Lucent, Pelephone, NTT, etc.
	\item Systems Integration and Test (part of various feature teams, product dev)
	\item CDMA base station development (C/C++) 
\end{zitemize}